Meta-analysis of fungicide application timing experiments for powdery mildew

### 2020-05-20 06_Publication_wireframe_and_7_Questions.Rmd
More edits

The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.  
Trial data had to include the date when powdery mildew was first observed. 
Trials needed to include either demethylase inhibitor (DMI), tebuconazole or propiconazole.

All trials included in this analysis were not previously published in peer-reviewed literature.
Some trials and results were reported online via the Grains Research and Development Corporation.

While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design. 
Some variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.

To reduce confounding effects of various fungicides we only included treatments within trials which used a DMI as a fungicide active, such as tebeconazole and propiconazole. 
Fungicide active from the DMI group was the main inclusion factor for the analysis which reduced the number of trials from 26 to 17 experiments.

Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref]. 
The 2013 NGA trials however, reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 - 9 scale.

@@

Response variables were averaged in trials which we had access to the raw data. 
For the remainder of the trial data except two trials, Gatton 2012 and Emerald 2015, only the treatment means and variance were reported. 
Gatton and Emerald trials were were only able to obtain treatment means without accompaning variance. 
For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})}) $  
Where MSE is the mean squared error of each trial.

$v_i = MSE_{y}/(n * Y_{i}^2) $

@@

PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(year = unique(year),
             location = unique(location),
             planting_date = unique(planting_date),
             first_sign_disease = unique(first_sign_disease))%>%
   arrange(year)%>%
   mutate(Research_org = c(rep("Queensland DAF",times =4),
                           rep("Northern Growers Alliance", times = 4),
                           rep("Queensland DAF",times =4),
                           rep("USQ", times = 5))) %>%
   kable(caption = "Table 1: Description of Experiments")%>%
   kable_styling(fixed_thead = TRUE,
                 full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```
## Results

>>>>

The criteria for inclusion of trial data in the meta-analysis required, a field trial testing fungicide efficacy for powdery mildew control on mungbean in the northern grains regions of eastern Australia.  
Trial data had to include: the date when powdery mildew was first observed; disease incidence at the end of the growing season; fungicide application dates; and crop yield. 
A total of 26 trials were collated and from these trials we selected the most frequently tested fungicides that had the same mode of action. 
The data were subset to only include treatments using demethylase inhibitor (DMI) fungicides, tebuconazole and propiconazole to reduce confounding effects of fungicides with varying modes of action. Subsequently the 26 trials were reduced to 17 using the same fungicide doses.

All trials included in this analysis were a randomised complete block design and not previously published in peer-reviewed literature.
Some trials and results were reported online via the Grains Research and Development Corporation.

While the main aim of all the trials collected for this study were to assess the efficacy of fungicide for control of powdery mildew, some trials  included additional variables in the experimental design. 
These additional variables included: row spacing, fungicide active ingredient, fungicide dose, planting date, number of fungicide applications, cultivar and  supplimentary irrigation, in addition to trial location and season.
To account for this variation between trials, and the treatments within trials, a single 'trial' factor was created to describe the main variables; trial location, trial season, host genotype and row spacing.

Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [Table_PMScale]. 
The 2013 NGA trials however, reported incidence as the percentage of leaves covered by powdery mildew and the location of the infected leaves in the canopy; lower, middle or upper canopy. 
Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was strait-forward to calculate the equivalent incidence on the ordinal 1 - 9 scale.

@@

For the trials which we had raw data, mean grain yields for each were calculated and the mean squared error within trial obtained from an anova of each study.
For the remainder of the trial data only the treatment means and variance were reported, except for Gatton in 2012 and Emerald in 2015. 
The Gatton and Emerald trials only reported treatment means without accompaning variance. 
For these trials the trial variance was imputed by randomly sampling the trial mean squared error from a distribution of log trial MSE.  
$rnorm(\overline{x}_{log(MSE_{1}) \dots, log(MSE_{n})}, \sigma_{log(MSE_{1}) \dots, log(MSE_{n})})$  
Where $MSE$ is the mean squared error of each trial and $n$ is the total number of trials.

Sample variance was computed from the trial MSE using the following equation, where $i$ is the $i$th trial, n is the number of replicates and $\overline{Y}$ is the mean grain yield for that treatment.  
$v_i = MSE_{i}/(n_{i} * \overline{Y}_{i}^2)$

@@

PM_Mdat %>%
   filter(fungicide_ai == "tebuconazole" | fungicide_ai == "propiconazole") %>%
   group_by(trial_ref) %>%
   summarise(year = unique(year),
             location = unique(location),
             planting_date = unique(planting_date),
             first_sign_disease = unique(first_sign_disease))%>%
   arrange(year)%>%
   mutate(Research_org = c(rep("Queensland DAF",times =4),
                           rep("Northern Growers Alliance", times = 4),
                           rep("Queensland DAF",times =4),
                           rep("USQ", times = 5))) %>%
   kable(caption = "Table 1: Description of Experiments")%>%
   kable_styling(fixed_thead = TRUE,
                 full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
```

```{r}
data.frame(Scale = 1:9,
           `Scale Description` = c("No sign of powdery mildew",
                                "Small colonies in lower 1/3 of canopy, up to 75% of plants affected",
                                "Colonies in lower 1/2 of canopy, > 75 % of plants affected",
                                "Colonies in lower 2/3 of canopy, up to 75 % of plants affected",
                                "Colonies in lower 2/3 of canopy, > 75 % of plants affected",
                                "Colonies in lower 2/3 of canopy, 100 % of plants affected",
                                "Colonies in lower 2/3 of canopy, 100 % of plants, with some plants with colonies in the top 1/3 of canopy",
                                "Colonies to top of the plant with > 75 % of plants affected",
                                "Colonies to top of the plant with > 100 % of plants affected and heavy leaf drop"
                                )) %>%
   kable(caption = "Table 2: Powdery Mildew severity scoring scale")%>%
   kable_styling(fixed_thead = T, full_width = T)
```

## Results
